% cv-us.tex
% $Id: cv-us.tex, v0.4 1/02/2024 09:47:18 Sylvain Bougerel$
%
% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2006 Jason R. Blevins
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents, however, I do ask that you
% please leave this notice and the above URL in the source code if you
% choose to redistribute this file.
%
% Jason R. Blevins <jrblevin@sdf.lonestar.org>
% http://jrblevin.freeshell.org
% Durham, December 12, 2006
%
%----------------------------------------------------------------------------%
% Copyright (C) 2007-2024 Sylvain Bougerel
%
% Modification for personal use. You are granted the same right as in the
% original document (see above). Likewise, the name of the orginial author
% and my name, and both copyrights should be left in the source code.
%
% Sylvain Bougerel <sylvain.bougerel.devel@gmail.com>
%
%%---------------------------------------------------------------------------%
%
% Notes:
%
% * Don't forget to change `pdfauthor' and `keywords' in the \hypersetup
%   section below.
%
% * To create a new page use: \newpage \opening
%
% * res.cls includes an \address{} command which can be used up to twice,
%   but my address is too long for the format it uses.
%
% * Alternate documentclass statement to put headings in margin:
%   \documentclass[margin,line,11pt,final]{res}
%
% * Can divide publication/presentation list into subsections by year:
%   \section{\bf\small\hspace{8mm}2006}
%
%%----------------------------------------------------------------------------%

\documentclass[overlapped,line]{res}

\usepackage{ifpdf}

\ifpdf
\usepackage[pdftex]{hyperref}
\else
\usepackage[hypertex]{hyperref}
\fi

\usepackage{tikz}
\usepackage{fontawesome}

\hypersetup{
  linkcolor=blue,
  colorlinks,
  urlcolor=blue,
  pdfpagemode=UseNone,
  pdftitle={Curriculum Vitae},
  pdfauthor={Sylvain Bougerel},
  pdfcreator={$ $Id: cv-us.tex, v0.4 1/02/2024 09:47:18 Sylvain Bougerel$ $},
  pdfsubject={Curriculum Vitae},
  pdfkeywords={Cloud Native AWS Python C++ Rust DevOps Continuous Integration Delivery
    Containers Kubernetes Terraform Linux Leadership Architect Design}
}

%% Thanks: https://tex.stackexchange.com/questions/99316/symbol-for-external-links
\newcommand{\ExternalLink}{%
    \tikz[x=1.2ex, y=1.2ex, baseline=-0.05ex]{%
        \begin{scope}[x=1ex, y=1ex]
            \clip(-0.1,-0.1)
                --++ (-0, 1.2)
                --++ (0.6, 0)
                --++ (0, -0.6)
                --++ (0.6, 0)
                --++ (0, -1);
            \path[draw,
                line width = 0.5,
                rounded corners=0.5]
                (0,0) rectangle (1,1);
        \end{scope}
        \path[draw, line width = 0.5] (0.5, 0.5)
            -- (1, 1);
        \path[draw, line width = 0.5] (0.6, 1)
            -- (1, 1) -- (1, 0.6);
          }
        }
\newcommand{\hrefa}[2]{\href{#1}{#2\,\ExternalLink}}

%%===========================================================================%%

\begin{document}

%---------------------------------------------------------------------------

% Make lists without bullets and with no indentation
\setlength{\leftmargini}{0em}
\renewcommand{\labelitemi}{}

% Use large bold font for printed name at top of pages
\renewcommand{\namefont}{\large\textbf}

%---------------------------------------------------------------------------

\name{Sylvain Bougerel}
\address{10 Martaban Road\\
  \#03-02 Ecoville\\
  Singapore 328668
}
\address{tel: +65 96673473\\
  \href{mailto:sylvain.bougerel@gmail.com}{sylvain.bougerel@gmail.com}\\
  \href{https://sg.linkedin.com/in/sylvain-bougerel-397b221}{linkedin}\,
  \href{https://github.com/sbougerel}{github}
}

\begin{resume}

  %---------------------------------------------------------------------------

  %\section{\bf Background}

  A decade of experience building software for other engineers at scale and in
  mission critical environments. Proponent of automation, CI/CD, GitOps and
  IaC. Open-source contributor and maintainer. Manager and mentor for hundredth
  of engineers.

  %---------------------------------------------------------------------------

  \section{\bf Recent Professional Experience}

  \begin{format}
    \title{l}\dates{r}\\
    \employer{l}\location{r}\\
    \body\\
  \end{format}

  \title{\em Principal Software Engineer}
  \employer{Grab (\hrefa{http://www.grab.com}{grab.com})}
  \location{Singapore}
  \dates{Mar 2020--Aug 2023}
  \begin{position}
    SOC
    Key rotation for Gitlab
    For our service infrastructure team, ported the Jenkins upgrade process from Ansible to Packer and Terraform, to reduce.
  \end{position}

  \title{\em Software Engineering Lead}
  \employer{Grab (\hrefa{http://www.grab.com}{grab.com})}
  \location{Singapore}
  \dates{Mar 2017--Mar 2020}
  \begin{position}
    Conveyor
    Gitlab
  \end{position}

  \title{\em Project Manager}
  \employer{Thales Solution Asia Pte Ltd
    (\hrefa{http://www.thalesgroup.com}{www.thalesgroup.com})}
  \location{Singapore}
  \dates{2015--Feb 2017}
  \begin{position}
    Took over full scope of the software project
    \hrefa{https://en.wikipedia.org/wiki/North_East_MRT_line}{NEL Upgrade} (The
    \hrefa{https://en.wikipedia.org/wiki/SCADA}{SCADA} interfacing all of its
    \hrefa{https://en.wikipedia.org/wiki/North_East_MRT_line\#Infrastructure}{infrastructure}).
    Maintained a positive relationship with our customer that contributed to increase the project's
    gross margin YoY by 2\%, from 21.5\% to 23.5\% through additional S\$400k
    in sales, valuing the project to 21.9 millions.
  \end{position}

  \title{\em Software Manager}
  \employer{Thales Solution Asia Pte Ltd
    (\hrefa{http://www.thalesgroup.com}{www.thalesgroup.com})}
  \location{Singapore}
  \dates{2011--2015}
  \begin{position}
    Headed the scrappy development team since the commencement of NEL upgrade
    (see above) as a hands-on Manager. Team averaged 6 Software Engineers (11 at
    peak) half of which I hired. Key contributor to delivering the project's
    milestones on target (15 days of delay on the project acceptance milestone
    after nearly 3 years of work). 17 Data centers, 24/7 critical operations, >3
    million LoC ported from \hrefa{https://en.wikipedia.org/wiki/HP-UX}{HP-UX}
    to Linux.
  \end{position}

  \title{\em Senior Software Engineer}
  \employer{Thales Security Asia Pte Ltd
    (\hrefa{http://www.thalesgroup.com}{www.thalesgroup.com})}
  \location{Singapore}
  \dates{Up to 2011}
  \begin{position}
    Worked with cross-continent teams to test and commission
    \hrefa{https://servicemix.apache.org/}{ServiceMix} interfaces for
    \hrefa{https://en.wikipedia.org/wiki/Command_and_control}{Command \&
      Control} centres of
    the \$450 million project \hrefa{https://www.youtube.com/watch?v=tvD9NkpsNas}{Mexico Ciudad Segura}. Also built the \hrefa{https://en.wikipedia.org/wiki/Automatic_vehicle_location}{AVL} component almost single-handedly, to track ~25000 vehicles pinging every 1-5 minutes. A simple distributed service component backed by PostgreSQL with stored procedures exceeded the requirements.
  \end{position}


  %----------------------------------------------------------------------------

  \section{\bf Recent Certifications}

  \begin{format}
    \title{l}\dates{r}\\
    \body\\
  \end{format}

  \title{\em Certified AWS Solution Architect Associate}
  \dates{January 2021}
  \begin{position}
    \hrefa{https://www.credly.com/badges/287f94f4-3c65-4765-b58e-91ea5781a06f}{Verify my badge here.}
  \end{position}

  %---------------------------------------------------------------------------

  \section{\bf Education}

  \begin{format}
    \title{l}\dates{r}\\
    \body\\
  \end{format}

  \title{\em Master of Science in Software Engineering}
  \dates{2003--2005}
  \begin{position}
    University of Technology of Belfort-Montb\'{e}liard, France\newline
    Final year exchange program at the National University of Singapore
  \end{position}

  \title{\em Bachelor of Science in Software Development}
  \dates{2000--2002}
  \begin{position}
    University of Paris, South, Science Faculty of Orsay, France
  \end{position}

  %------------------------------------------------------------------------------

  \section{\bf Details of Recent Projects}

  \begin{format}
    \title{l}\dates{r}\\
    \body\\
  \end{format}

  \title{\em North East Line ISCS Upgrade (NEL Upgrade)}
  \dates{July\ 2011--Present}
  \begin{position}
    The North-East Line ISCS enables only 6 operators to run the entire fleet of
    32 driver-less trains, monitor the 40km of tracks, the various energy
    circuits (air, water, electricity) and efficiently communicate among
    operators, contractors and the public. With it's very large number of
    interfaces and its direct impact on the population, this upgrade is a
    critical undertaking.
    \newline
    {\bf Technologies:} JIRA, Git, Jenkins, VMWare, Sikuli, Linux, C++, Tcl/Tk, Python, Gdb.
  \end{position}

  \title{\em Mexico Ciudad Segura}
  \dates{October\ 2009--June\ 2011}
  \begin{position}
    In 2009, Thales Group has been awarded with the deployment of a new
    integrated call center and security system for Mexico City.  This was
    Thales' largest integrated call center ever to be rolled out. Some key
    figures: 6 operation centers to deploy, 8000 cameras to control, 25000
    ground resources to manage, 40000 calls received per day, 8 Millions people
    to protect.
    \newline
    {\bf Technologies:} JIRA, SVN, C\# (with .Net components WCF, WPF, LinQ), TFS, MSSQL, ActiveMQ,
    ServiceMix.
  \end{position}

  \title{\em New Coastal Surveillance System}
  \dates{May\ 2008--September\ 2009}
  \begin{position}
    The new system is designed to provide a greater level of high-availability,
    scalability and ease of development. In 2013, this product became the basis
    of our offer in costal surveillance systems and has been sold to 3
    governmental organisations since.
    \newline
    {\bf Technologies:} SVN, ActiveMQ JMS, XSD, C++, Boost (Asio), Java, Python, Linux,
    Gdb, Valgrind.
  \end{position}

  \title{\em Singapore Police Coast Guard}
  \dates{May\ 2006--April\ 2008}
  \begin{position}
    The supervision system monitoring the maritime traffic of
    Singapore waters. The system fuses the data from 5 main radars and
    several mobile radars in order to render a syntetic view of the 2000
    marine vessels circulating in the busy waters of Singapore.
    \newline
    {\bf Technologies:} Linux, C++, Lex/Yacc, OpenVZ, Valgrind, Gdb, X11/Motif.
  \end{position}

  % ---------------------------------------------------------------------------

  \section{\bf Personal Information}
  French national and Singapore Permanent Resident. Born on 23rd September 1981. Fluent in English and French.

  %---------------------------------------------------------------------------

  \section{\bf Personal Projects and fun}

  Emacsen Passionate about Linux and open-source, working since 2009 on the
  open-source Spatial C++ Library, the spiritual child of the library
  libkdtree++, which I maintained for a short period of time.

  %---------------------------------------------------------------------------

\end{resume}

\end{document}

%%===========================================================================%%
